Paper \#ZW10157

### 2019-01-30 paper/submission/ZW10157-response-1.tex

At the same time, AWA is a facility where many different accelerator research experiments take
place. Therefore it is very desirable, and was an important research objective, to develop a precise, e.g. 3D
model embedded into a multi-objective optimization framework. In this way, optimization of various 
machine configurations can be done at different charge levels. While other codes such as GPT [updated ref here] and ELEGANT [updated ref here], also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e. free to use), massively parallel, and fully 3D.
}

@@

=======
\documentclass{article}
\usepackage{latexsym}
\usepackage{color}
\setlength{\parskip}{3mm}
\setlength{\parindent}{0pt}
\usepackage[margin=1in]{geometry}

With the best regards  \\[3mm]

{\bf Our response:} {\color{blue} The code examples in sections IV-V have been removed.}

{\bf Our response:} {\color{red} The AWA is a high charge charge accelerator. The strong non-linearities
justifying the full 3D approach. At the same time AWA is a facility where many different accelerator research experiments take
place. Therefore it is very desirable, and was one of the important research objectives, to come up with a precise, e.g. 3D
model embedded into a multi-objective optimisation framework. The OPAL framework, differentiates itself, being massively paralle,
full 3D and, and simple to use i.e.\ user friendly.}

{\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
	Especially the following:

	We thank the reviewer for the list of references. 
	References described or referenced by A. Hofler in the above were excluded from 
	the bibliography. 
}

1) References for 4 PISA-based optimization systems:

{\color{blue}{Included in updated bib:}}

{\color{blue}{Exluded from bib, because  they are in A. Hofler 13':}}

2) Optimization systems using NSGA-II (a few example references):

M. Borland et al. PAC 2009, Vancouver, BC, Canada, May 2009, TH6PFP062

3) Survey with various references showing GA/EA usage in Accelerator
Physics: A. Hofler. “Genetic Algorithms and Their Applications in
Accelerator Physics,” NAPAC2013, Pasadena, CA, USA, 2013, THTB1

{\bf Our response:} {\color{red} The statements on the lines  17-19 of our initial submission are misleading, as
the referee correctly recognised. We replace them with the following:

Despite the great success of on-line models, and various model dependent and model independent tuning and 
optimisation techniques, in research facilities such as AWA empirical tuning is still one of the methods used. Due to the 
non-linear problem mainly from space charge, simple and fast models are applicable only in a very 
restricted manner. When it comes to multi-objective optimisation then the situation is even more complicated.
}

{\bf Our response:} {\color{blue} XXXXX.}

That said, a general-purpose optimization system is a useful addition
to the design tools for accelerators. The way to entice prospective
users through PRAB is to introduce the system with a very brief
general overview and then focus on the results obtained using the
system. The detailed discussion of the design and implementation with
code snippets should be provided as Supplemental Material. PRAB is not
a computer journal. Salient implementation or design points if
necessary can be summarized in short Appendices; the main discussion
of the paper should be the optimization results not the details of the
implementation and design. For example, in the main text, it is
reasonable to say that the optimization system provides a flexible and
extensible meta-language for setting up optimization problems (covered
in detail in Section III subsection E) and then direct the reader to
an Appendix or the Supplemental Material for the details provided in
Section III subsection E. Bear in mind, though, that several of the
PISA-based systems mentioned above, also, provide expression
capabilities and should be referenced. The one presented here is more
flexible and has the advantage of being easily extended. Both are
distinguishing features. The authors need to emphasize what
differentiates their system from 13+ years of development in the area
of GA/EA-based optimization in accelerator design and then demonstrate
that the results produced are exemplary or could not have been
produced otherwise. Or they should focus on how their system advances
the application of the target AWA machine (the Gulliford references
use this approach).

The high charge beam line at the Argonne Wakefield Accelerator
Facility was used as the beam dynamics model. The 3D beam size,
transverse momentum, and energy spread were optimized.

{\bf Our response:} {\color{blue} XXX}

{\bf Our response: } {\color{red} This section has being shortened. However we would like to 
leave the existing description, in order to drive home the fact that the framework can be 
easily extended with other optimisation algorithms. Something that you can not find in most of the 
existing codes.}`

>>>>

At the same time, AWA is a facility where many different accelerator research experiments take
place. Therefore it is very desirable, and was an important research objective, to develop a precise, e.g. 3D
model embedded into a multi-objective optimization framework. In this way, optimization of various 
machine configurations can be done at different charge levels. While other codes such as GPT [updated ref here] and ELEGANT [updated ref here], also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e. free to use), massively parallel, and fully 3D.

A hallmark of the AWA facility is the flexibility to swap physical
components in the beamlines, which enables different, often novel,
accelerator research experiments to take place.  Not only do the
physical machine components change, the beam characteristics also vary
considerably to meet different needs.  The facility operates at both low
and high charge (up to 100 nC), and at high charge strong nonlinearities
require a full 3D space charge approach in simulations for modeling.  
Finding optics solutions in this regime, especially when
there are additional constraints such as the small aperture two-beam
accelerating structures, is challenging even without the quick
turnaround of the beamline configurations.  Therefore, it has been an
important research objective to develop a precise, e.g. 3D model
embedded into a multi-objective optimization framework that may be used
as a flexible platform for optimization of changing machine
configurations operated at different charge levels. While other codes
such as GPT [updated ref here] and ELEGANT [updated ref here], also have
integrated genetic optimization algorithms; the OPAL framework,
differentiates itself by being open source (i.e. free to use), massively
parallel, and fully 3D.

}

@@
